Characterizing Stellar Streams by ML

### 2023-08-21 src/tex/ms.tex
[showyourwork] overleaf sync

\documentclass[twocolumn]{aastex631}
\usepackage{showyourwork}
\usepackage{amsmath}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage{dsfont}
\usepackage{todonotes}

@@

        \begin{figure*}
            \script{mock/plot/results.py}
            \centering
            \includegraphics[width=1\linewidth]{figures/mock/results.pdf}
            \caption{Caption: .}
            TODO:
            \begin{enumerate}
                \item the linear density in the stream-fraction plot
            \end{enumerate}
            \label{fig:mock_data_result}
        \end{figure*}

@@

            \variable{output/gd1/select_members.tex}

@@

    The data availability statement is modified from

@@

        \package{asdf} \citep{Greenfield2015},
        \package{astropy} \citep{Astropy2013, Astropy2018, Astropy2022},
        \package{astroquery} \citep{Astroquery2019},
        \package{Matplotlib} \citep{Hunter2007},
        \package{NumPy} \citep{Harris2020},
        \package{Pytorch} \citep{Pytorch2019},
        \package{SciPy} \citep{Scipy2020},

@@

    This study was carried out using the reproducibility software
    \href{https://github.com/showyourwork/showyourwork}{\showyourwork}
    \citep{Luger2021}, which uses continuous integration to
    programmatically download the data, perform the analyses, create the
    figures, and compile the manuscript. Each figure caption contains two links:
    one to the dataset used in the corresponding figure, and the other to the
    script used to make the figure. The datasets are stored at
    \todo[inline]{zenodo url}. The git repository associated
    with this study is publicly available at $\GitHubURL{}$.

>>>>

\documentclass[twocolumn]{aastex631}
\usepackage{showyourwork}
\usepackage{amsmath, amssymb}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage{dsfont}
\usepackage[inline]{enumitem}
\usepackage{todonotes}

@@

        \begin{figure*}
            \script{mock/plot/results.py}
            \centering
            \includegraphics[width=1\linewidth]{figures/mock/results.pdf}
            \caption{
                %
                \textbf{Top panel:}%
                The stream mixture coefficient $f(\phi_1)$ 
                Stream fraction.
                %
                \textbf{Middle panel:}%
                $\phi_2(\phi_1)$
                %
                \textbf{Lower panel 3:}%
                %
                \textbf{Upper Histograms:}%
                %
                \textbf{Upper Middle Histograms:}%
                %
                \textbf{Lower Middle Histograms:}%
                %
                \textbf{Lower Histograms:}%
            }
            TODO:
            \begin{enumerate}
                \item the linear density in the stream-fraction plot
            \end{enumerate}
            \label{fig:mock_data_result}
        \end{figure*}

@@

            \variable{output/gd1/member_table_select.tex}

@@

    The data availability statement is modified from one provided to ShowYourWork by Mathieu Renzo.

@@

        \package{asdf} \citep{Greenfield2015},
        \package{astropy} \citep{Astropy2013, Astropy2018, Astropy2022},
        \package{astroquery} \citep{Astroquery2019},
        \package{Matplotlib} \citep{Hunter2007},
        \package{NumPy} \citep{Harris2020},
        \package{Pytorch} \citep{Pytorch2019},
        \package{SciPy} \citep{Scipy2020},
        \package{ShowYourWork} \citep{}

@@

    This study was carried out using the reproducibility software
    \href{https://github.com/showyourwork/showyourwork}{\showyourwork}
    \citep{Luger2021}, which uses continuous integration to
    programmatically download the data, perform the analyses, create the
    figures, and compile the manuscript. Each figure caption contains two links:
    one to the dataset used in the corresponding figure, and the other to the
    script used to make the figure. The datasets are stored at
    \todo[inline]{zenodo url}. The git repository associated
    with this study is publicly available at \GitHubURL{}.
